### 2017-05-18 sheets/basis-2/sheet-basis-2.tex
More extensions.
Yet more fixes.

\begin{answer}
  \begin{enumerate}
  \item A subcategory of an ordered set $(S,\leq)$ is an ordered set $(S',\leq')$ such that $S'\subseteq S$ and $\leq'\;\subseteq\;\leq$.
  \item The subcategories of a group are either the category with no objects or submonoids of the group (which is of course a monoid). The only full subcategories are the group itself and the category with no objects. 
  \end{enumerate}
\end{answer}

@@

\begin{exercise}
  Let $A$ and $B$ be posets, and $\A$ and $\B$ be the corresponding categories. Consider a contravariant functor $F:\A\rightarrow \B$. Describe properties of the corresponding function $f:A\rightarrow B$.
\end{exercise}

@@

  Now, suppose $g$ is a group homomorphism satisfying $g\of i=j$. 
  Let $a_1\cdots a_n\in A^*$. Proof by induction on $n$ that $g(n)=f(n)$.

  Base case: $g(\epsilon)=0_M$ because $\epsilon$ is the neutral element in $A^*$).

@@

\begin{answer}
  \begin{enumerate}
  \item Consider $\A$ given by
    \[
      \begin{tikzcd}[column sep=huge,row sep=huge]
        E\arrow[r,yshift=.85ex,"s"] \arrow[r,below,yshift=-.85ex,"e"]&V
      \end{tikzcd}
    \]
    Then a functor $F\from \A\to\Set$ assigns to both $E$ and $V$ sets $E'$ and $V'$ (which correspond to the set of edges and vertices respectively) and to $s,e$ functions $s'$ and $e'$ that take edges $d$ from $E'$ and return elements $s'(d)$ and $e'(d)$ which correspond to the start and end node of the edge $d$ respectively.
  \item Consider $\B$ given by
    \[
      \begin{tikzcd}[column sep=huge,row sep=huge]
        A\arrow[r,yshift=.85ex,"f"] & B\arrow[l,below,yshift=-.85ex,"g"] \arrow[loop right,"h"]
      \end{tikzcd}
    \]
    (plus the identities) such that $g\of f=1_A$, $f\of g=h$, $g\of h=g$ and $h\of f=f$. Then any functor $F\from\A\to\Set$ maps $A$ and $B$ to sets $A'$ and $B'$ respectively and $f$ is mapped to a function $f'\from A'\to B'$ and $g$ is mapped to a function $g'\from B'\to A'$ such that for all $a\in A'$, $g'(f'(a))=a$. Thus $f$ is an injection.
  \end{enumerate}
\end{answer}

>>>>

\begin{answer}
  \begin{enumerate}
  \item A subcategory of an ordered set $(S,\leq)$ is an ordered set $(S',\leq')$ such that $S'\subseteq S$ and $\leq'\;\subseteq\;\leq$. In the case of full subcategories even $\leq'\;=\;\leq$ holds.
  \item The subcategories of a group are either the category with no objects or submonoids of the group (which is of course a monoid). The only full subcategories are the group itself and the category with no objects. 
  \end{enumerate}
\end{answer}

@@

\begin{exercise}
  Let $A$ and $B$ be posets, and $\A$ and $\B$ be the corresponding categories. Consider a contravariant functor $F:\A^{\op}\rightarrow \B$. Describe properties of the corresponding function $f:A\rightarrow B$.
\end{exercise}

@@

  Now, suppose $g$ is a group homomorphism satisfying $g\of i=j$. 
  Let $a_1\cdots a_n\in A^*$. Proof by induction on $n$ that $g(a_1\cdots a_n)=f(a_1\cdots a_n)$.

  Base case: $g(\epsilon)=0_M=f(\epsilon)$ because $\epsilon$ is the neutral element in $A^*$).

@@

\begin{answer}
  \begin{enumerate}
  \item Consider $\A$ given by
    \[
      \begin{tikzcd}[column sep=huge,row sep=huge]
        E\arrow[r,yshift=.85ex,"s"] \arrow[r,below,yshift=-.85ex,"e"]&V
      \end{tikzcd}
    \]
    Then a functor $F\from \A\to\Set$ assigns to both $E$ and $V$ sets $E'$ and $V'$ (which correspond to the set of edges and vertices respectively) and to $s,e$ functions $s'$ and $e'$ that take edges $d$ from $E'$ and return elements $s'(d)$ and $e'(d)$ which correspond to the start and end node of the edge $d$ respectively.
  \item Consider $\B$ given by
    \[
      \begin{tikzcd}[column sep=huge,row sep=huge]
        A\arrow[r,yshift=.85ex,"f"] & B\arrow[l,below,yshift=-.85ex,"g"] \arrow[loop right,"h"]
      \end{tikzcd}
    \]
    (plus the identities) such that $g\of f=1_A$, $f\of g=h$, $g\of h=g$ and $h\of f=f$. Then any functor $F\from\A\to\Set$ maps $A$ and $B$ to sets $A'$ and $B'$ respectively and $f$ is mapped to a function $f'\from A'\to B'$ and $g$ is mapped to a function $g'\from B'\to A'$ such that for all $a\in A'$, $g'(f'(a))=a$. Thus $f'$ is an injection.

    Indeed, the reverse is also true: Given any injection $f'\from A'\to B'$ there is functor $F\from \A\to\Set$ such that $f'$ corresponds to $F$ (in the way specified above).
  \end{enumerate}
\end{answer}
